\textbf{\supplement}\vskip 2ex \mytitle\vskip 2ex

### 2023-06-08 expanded-appendix.tex
Trying to get Elsevier's Latex processing to work
Fixing Elsevier quirks

@@

\@writefile{toc}{\contentsline {subsection}{\numberline {12.a}Selected journal case studies}{52}{subsection.12.1}\protected@file@percent }
\@writefile{toc}{\contentsline {subsubsection}{\numberline {12.a.1}\emph  {The Lancet\/}}{52}{subsubsection.12.1.1}\protected@file@percent }

@@

\@writefile{lot}{\contentsline {table}{\numberline {6}{\ignorespaces Conforming to the RAP{\tt  +}\ methodology, the abbreviated summary above was generated automatically, by using \texttt  {make data}. A full list of \texttt  {make} options is generated by \texttt  {make} or \texttt  {make help} when run on the Unix command line. }}{53}{table.6}\protected@file@percent }
\newlabel{supplement-table:options}{{6}{53}{Conforming to the \RAPstar \ methodology, the abbreviated summary above was generated automatically, by using \texttt {make data}. A full list of \texttt {make} options is generated by \texttt {make} or \texttt {make help} when run on the Unix command line}{table.6}{}}

@@

@@

\@writefile{toc}{\contentsline {subsubsection}{\numberline {12.c.2}Sample assessment and scoring}{58}{subsubsection.12.3.2}\protected@file@percent }

@@

\contentsline {subsection}{\numberline {12.a}Selected journal case studies}{52}{subsection.12.1}%
\contentsline {subsubsection}{\numberline {12.a.1}\emph {The Lancet\/}}{52}{subsubsection.12.1.1}%

@@

\contentsline {subsubsection}{\numberline {12.c.2}Sample assessment and scoring}{58}{subsubsection.12.3.2}%

@@

\begin{figure} 
   \centering
   \includegraphics[width=5in]{generated/basic.\imageFileSuffix} 
   \caption{The common basic --- error-prone and obsolete --- approach to scientific authoring is to use code to help generate analyses and diagrams, then manually copy and paste the selected results into the publication. Note that the publication, including the results, can be edited arbitrarily, and typically the results published will have been edited and modified (if only for typographical purposes) from those actually generated by the code.}
   \label{supplement-fig:basic}
\end{figure}
\begin{figure} 
   \centering
   \includegraphics[width=5in]{generated/excel.\imageFileSuffix} 
   \caption{When the code is in a spreadsheet, such as Microsoft Excel, the code is generally hidden from sight. The data copied \& pasted into a publication may or may not be calculated from data in other cells (such as column totals). Records are rarely taken of these manual processes, and, anyway, typically it is impossible to be certain exactly what has been copied unless very great care is taken. In consequence, if a spreadsheet is modified, it is haphazard what results are updated and corrected in the publication. }
   \label{supplement-fig:excel}
\end{figure}
\begin{figure} 
   \centering
   \includegraphics[width=5in]{generated/import.\imageFileSuffix} 
   \caption{Improving over the normal approach (figure \ref{supplement-fig:basic}), data and diagrams are placed in the publication using a programmed, systematic approach. In the present paper, this was done by generating text files of \LaTeX\ definitions (represented by boxes in the central column of the schematic), hence providing \LaTeX\ names for all of the code-generated values. Since the copying of results into a publication is automated and easy, any improvements to the results (such as correcting errors) are made by improving the code --- which therefore contributes to improving all future-generated results too. Not shown, but in well-engineered code, documentation will also be generated, such as by using tools such as JavaDoc or Doxygen.}
   \label{supplement-fig:rap}
\end{figure}
\begin{figure}[t]
   \centering
   \includegraphics[width=5in]{generated/notebook.\imageFileSuffix} 
   \caption{In a notebook system, such as \emph{Mathematica\/} or Jupyter, a single document --- the notebook --- integrates the publication, the code, any notes, as well as all the results. The code generates results and images that are automatically (and reliably) inserted in place into the notebook, usually right after the code that generates them. Some parts of the notebook are marked or selected to be printed as the publication, thus allowing most if not all code to be hidden from the final publication. In well-engineered code, the notebook will directly contain full documentation.
Note that in most systems, notebooks can import and generate arbitrary data (images, sounds, sensor data, etc).}
   \label{supplement-fig:notebook}
\end{figure}

@@

\begin{table}[t]
\begin{center}
% expand generated/make-help.tex
% Edit makefile to change the selected make command choices, as follows:
% 1 - make all
% 2 - make archive
% 3 - make check-same
% 4 - make check-update
% 5 - make check-versions
% 6 - make data
% 7 - make expand
% 8 - make git-prep
% 9 - make help
% 10 - make help-brief
% 11 - make mathematica
% 12 - make mathematica-open
% 13 - make one-file
% 14 - make pdf
% 15 - make push
% 16 - make readme
% 17 - make really-tidyup
% 18 - make tidyup
% 19 - make zip
% 20 - make zip-data

@@

\texttt{make data}&
      Analyze the data, and generate all the data files, the Unix scripts, the CSV, and \LaTeX\ files (including the \LaTeX\ summary of this makefile), etc. This \texttt{make} option runs \texttt{node programs/data.js}, downloads the Git repositories used in the pilot survey, and then analyzes them. Note that downloading all the repositories in a reasonable time needs decent internet bandwidth.\\
   \multicolumn{1}{l@{\vdots}}{}&\\

>>>>

\@writefile{lot}{\contentsline {table}{\numberline {6}{\ignorespaces Conforming to the RAP{\tt  +}\ methodology, the abbreviated summary above was generated automatically, by using \texttt  {make data}. A full list of \texttt  {make} options is generated by \texttt  {make} or \texttt  {make help} when run on the Unix command line. }}{52}{table.6}\protected@file@percent }
\newlabel{supplement-table:options}{{6}{52}{Conforming to the \RAPstar \ methodology, the abbreviated summary above was generated automatically, by using \texttt {make data}. A full list of \texttt {make} options is generated by \texttt {make} or \texttt {make help} when run on the Unix command line}{table.6}{}}

@@

@@

\@writefile{toc}{\contentsline {subsection}{\numberline {12.a}Selected journal case studies}{53}{subsection.12.1}\protected@file@percent }
\@writefile{toc}{\contentsline {subsubsection}{\numberline {12.a.1}\emph  {The Lancet\/}}{53}{subsubsection.12.1.1}\protected@file@percent }

@@

\@writefile{toc}{\contentsline {subsubsection}{\numberline {12.c.2}Sample assessment and scoring}{57}{subsubsection.12.3.2}\protected@file@percent }

@@

@@

\contentsline {subsection}{\numberline {12.a}Selected journal case studies}{53}{subsection.12.1}%
\contentsline {subsubsection}{\numberline {12.a.1}\emph {The Lancet\/}}{53}{subsubsection.12.1.1}%

@@

\contentsline {subsubsection}{\numberline {12.c.2}Sample assessment and scoring}{57}{subsubsection.12.3.2}%

@@

\begin{figure} 
   \centering
   % removed generated/ from graphics pathname
\includegraphics[width=5in]{expanded-basic.\imageFileSuffix} 
   \caption{The common basic --- error-prone and obsolete --- approach to scientific authoring is to use code to help generate analyses and diagrams, then manually copy and paste the selected results into the publication. Note that the publication, including the results, can be edited arbitrarily, and typically the results published will have been edited and modified (if only for typographical purposes) from those actually generated by the code.}
   \label{supplement-fig:basic}
\end{figure}
\begin{figure} 
   \centering
   % removed generated/ from graphics pathname
\includegraphics[width=5in]{expanded-excel.\imageFileSuffix} 
   \caption{When the code is in a spreadsheet, such as Microsoft Excel, the code is generally hidden from sight. The data copied \& pasted into a publication may or may not be calculated from data in other cells (such as column totals). Records are rarely taken of these manual processes, and, anyway, typically it is impossible to be certain exactly what has been copied unless very great care is taken. In consequence, if a spreadsheet is modified, it is haphazard what results are updated and corrected in the publication. }
   \label{supplement-fig:excel}
\end{figure}
\begin{figure} 
   \centering
   % removed generated/ from graphics pathname
\includegraphics[width=5in]{expanded-import.\imageFileSuffix} 
   \caption{Improving over the normal approach (figure \ref{supplement-fig:basic}), data and diagrams are placed in the publication using a programmed, systematic approach. In the present paper, this was done by generating text files of \LaTeX\ definitions (represented by boxes in the central column of the schematic), hence providing \LaTeX\ names for all of the code-generated values. Since the copying of results into a publication is automated and easy, any improvements to the results (such as correcting errors) are made by improving the code --- which therefore contributes to improving all future-generated results too. Not shown, but in well-engineered code, documentation will also be generated, such as by using tools such as JavaDoc or Doxygen.}
   \label{supplement-fig:rap}
\end{figure}
\begin{figure}[t]
   \centering
   % removed generated/ from graphics pathname
\includegraphics[width=5in]{expanded-notebook.\imageFileSuffix} 
   \caption{In a notebook system, such as \emph{Mathematica\/} or Jupyter, a single document --- the notebook --- integrates the publication, the code, any notes, as well as all the results. The code generates results and images that are automatically (and reliably) inserted in place into the notebook, usually right after the code that generates them. Some parts of the notebook are marked or selected to be printed as the publication, thus allowing most if not all code to be hidden from the final publication. In well-engineered code, the notebook will directly contain full documentation.
Note that in most systems, notebooks can import and generate arbitrary data (images, sounds, sensor data, etc).}
   \label{supplement-fig:notebook}
\end{figure}

@@

\begin{table}[t]
\begin{center}
% expand generated/make-help.tex
% Edit makefile to change the selected make command choices, as follows:
% 1 - make all
% 2 - make archive
% 3 - make check
% 4 - make check-git
% 5 - make check-same
% 6 - make check-update
% 7 - make check-versions
% 8 - make data
% 9 - make expand
% 10 - make help
% 11 - make help-brief
% 12 - make mathematica
% 13 - make mathematica-open
% 14 - make one-file
% 15 - make pdf
% 16 - make push
% 17 - make readme
% 18 - make really-tidyup
% 19 - make tidyup
% 20 - make zip
% 21 - make zip-data

@@

\texttt{make check-versions}&
      Check that you have the right software and software versions to run everything.\\
   \multicolumn{1}{l@{\vdots}}{}&\\
